---
title: "SDG_MENARO_data_description"
format: docx
editor: visual
---

This code describes the compiled data for the MENARO SDG benchmarking project in UNICEF.

Unless noted, the data refers only to data from the 20 MENARO countries.

```{r}
#| echo: false
#| message: false

library(dplyr)
library(ggplot2)
library(knitr)
library(openxlsx)
library(tidyr)

load("output/indicator_data_WORLD.Rdata")

## MENARO countries ----
MENARO_metadata <- read.csv("source_data/MENARO_metadata.csv")

## SDG indicator series codes ----
#metadata of SDG child indicators. Includes the code in the SDG Global Database
CR_SDG_indicators <- read.xlsx("C:/Users/palma/OneDrive - UNICEF/MENARO SDG/child_related_SDG_indicators.xlsx",
                                sheet = "child_related_SDG_indicators")

indicator_data_MENARO <- indicator_data_WORLD |> filter(iso3 %in% MENARO_metadata$iso3)

indicator_metadata <- read.xlsx("C:/Users/palma/OneDrive - UNICEF/MENARO SDG/child_related_SDG_indicators.xlsx")
```

## Number of countries and points per indicator

```{r}
#| echo: false

points.per.indicator <- indicator_data_MENARO |> 
  group_by(MENARO.indicator.code) |> 
  reframe(Countries = length(unique(iso3)),
          First.Year = min(time.period),
          Last.Year = max(time.period),
          n.points = length(obs.value),
          n.points.2015 = length(obs.value[time.period>=2015])) |> 
  left_join(indicator_metadata |> select(MENARO.indicator.code, Benchmarking.indicators, SDG_INDICATOR), by = "MENARO.indicator.code") |> 
  select(SDG_INDICATOR, Benchmarking.indicators, Countries, First.Year, Last.Year, n.points, n.points.2015) 

points.per.indicator <- indicator_metadata |> select(SDG_INDICATOR, Benchmarking.indicators) |> left_join(points.per.indicator, by=c("SDG_INDICATOR", "Benchmarking.indicators"))|> 
  arrange(SDG_INDICATOR)

kable(points.per.indicator)
```

{{< pagebreak >}}

## Number of indicators per country

```{r}
#| echo: false

points.per.indicator.per.country <- indicator_data_MENARO |> 
  group_by(iso3, MENARO.indicator.code) |> 
  reframe(n.points = length(obs.value)) 

count.zeros <- as.data.frame(table(points.per.indicator.per.country$iso3, points.per.indicator.per.country$MENARO.indicator.code))

zeros.per.country <- count.zeros |> 
  group_by(Var1) |> 
  reframe(`Ind. w/o point` = sum(Freq==0)) |> 
  rename(iso3=Var1)

indicators.per.country <- points.per.indicator.per.country |> 
  group_by(iso3) |> 
  reframe(`Ind. w/1 point` = sum(n.points == 1),
          `Ind. w/2 point` = sum(n.points == 2),
          `Ind. w/3 point` = sum(n.points == 3),
          `Ind. w/4 point` = sum(n.points == 4),
          `Ind. w/5+ point` = sum(n.points > 4)) |> 
  left_join(zeros.per.country, by="iso3") |> 
  select(iso3, `Ind. w/o point`, `Ind. w/1 point`,
         `Ind. w/2 point`,`Ind. w/3 point`,`Ind. w/4 point`,
         `Ind. w/5+ point`)
  
kable(indicators.per.country)
```

## 1.1.1 Children living in households in extreme poverty

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SI_POV_DAY1")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 1.2.1 Children living below the national poverty line

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SI_POV_NAHC")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 1.2.2 Multidimensional poverty

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="PV_CHLD_DPRV_REG_MOD")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 1.3.1. Children covered by social protection

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SI_COV_CHLD")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 1.4.1 (1/2) At least basic drinking water

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SP_ACS_BSRVH2O")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 1.4.1 (2/2) At least basic sanitation

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SP_ACS_BSRVSAN")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 2.2.1 Stunting

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_STA_STNT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 2.2.2 Wasting

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_STA_WAST")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 2.2.2 Overweight

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SN_STA_OVWGT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.1.1 Maternal mortality ratio

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_STA_MORT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.1.2 Skilled Birth attendant

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_STA_BRTC")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.2.1 Under-5 mortality rate

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_DYN_MORT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.2.2 Neonatal mortality rate

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_DYN_NMRT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.3.1 HIV incidence, 15-19 years

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_HIV_INCD_15_19")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.3.1 HIV incidence, 0-14 years

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_HIV_INCD_U15")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.7.2 Adolescent birth rate

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SP_DYN_ADKL")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.8.1 Universal health coverage index

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_ACS_UNHC")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.b.1 (1/2) DTP3

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_ACS_DTP3")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 3.b.1 (2/2) MCV2

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_ACS_MCV2")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (1/6) Math, grade 2 or 3

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_1")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (2/6) Math, primary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_2")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (3/6) Math, lower secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_3")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (4/6) Reading, grade 2 or 3

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_4")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (5/6) Reading, primary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_5")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.1 (6/6) Reading, lower secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_PRFL_6")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.2 (1/3) Completion rate, primary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_CPLR_PR")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.2 (2/3) Completion rate, lower secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_CPLR_LS")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.2 (3/3) Completion rate, upper secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_TOT_CPLR_US")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.4 (1/3) Out-of-school rate, primary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="ED_ROFST_L1")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.4 (2/3) Out-of-school rate, lower secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="ED_ROFST_L2")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.1.4 (3/3) Out-of-school rate, upper secondary

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="ED_ROFST_L3")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.2.1 Developmentally on track

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_DEV_ONTRK")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 4.2.2 Net attendance rate

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SE_PRE_PARTN")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 5.1.1 Legal frameworks for gender equality

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SG_LGL_GENEQEMP")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 5.2.1 Sexual violence

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="VC_VAW_MARR")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 5.3.1 Child marriage

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SP_DYN_MRBF18")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 5.3.2 FGM

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_STA_FGMS")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 5.6.1 Informed decisions on reproductive health

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_FPL_INFMRH")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 6.1.1 Safely managed drinking water

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_H2O_SAFE")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 6.2.1 (1/3) Open defecation

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_SAN_DEFECT")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 6.2.1 (2/3) Basic hygiene

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_SAN_HNDWSH")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 6.2.1 (3/3) Safely managed sanitation

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SH_SAN_SAFE")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 8.7.1 Child labour

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="SL_TLF_CHLDEC")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 16.2.1 Violent discipline

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="VC_VAW_PHYPYV")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 16.2.3 (1/2) Sexual violence in childhood (female)

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="VC_VAW_SXVLN_F")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

{{< pagebreak >}}

## 16.2.3 (2/2) Sexual violence in childhood (male)

```{r}
#| echo: false
#| warning: false
#| message: false
indicator.data <- indicator_data_MENARO |> 
  filter(MENARO.indicator.code=="VC_VAW_SXVLN_M")
  
g <- ggplot(indicator.data, aes(x=time.period, y=obs.value, color=iso3))+
  geom_point()+
  geom_line()
print(g)
```

## 
